Argennon: A Scalable Smart Contract Platform

### 2022-04-16 tex/sections/elements.tex
Remove outdated parts
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

An Argennon transaction consist of an HTTP request made by a user, to an Argennon application and a resource
declaration object. Transactions can only be
issued by users and applications can not create transactions. An Argennon transaction is also called
an \emph{external request}.

@@

Every Argennon transaction needs to specify a maximum for
The Argennon protocol requires every  an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs. Every
transaction is required to specify two maximum execution costs: \texttt{maxInternalCost}
and \texttt{maxExternalCost}. The \emph{external} execution cost of a transaction is the \textbf{overall} cost of its
\texttt{invoke\_dispatcher} and \texttt{invoke\_later} instructions,\footnote{By overall cost, we mean the execution
cost needed for reaching the next instruction.}. The remaining execution cost will be considered as
the \emph{internal} cost. If a transaction reaches one of its maximum execution costs, executing any instruction
which has that type of cost, will throw an AVM exception.

\note{When a transaction reaches its \texttt{maxExternalCost}, it can still execute
its own code, while it can not call other smart contracts.
This way the execution cost of a smart contract is completely decoupled from the
smart contract it calls, and a malicious contract can not make its invoker certainly fail
by using infinite loops.}

Also, Argennon transactions are required to specify what heap or code area addresses they will access. This will
enable validators to parallelize transaction validation as we will see in Section~\ref{sec:concurrency}. An instruction
that tries to access a memory location that is not in the access list of the transaction, will throw an exception.
Users could use off-chain \emph{execution oracles} to predict the list of memory locations their transactions need.

An execution oracle is a full AVM emulator that keeps a full local copy of the AVM storage and can emulate AVM
execution without accessing a ZK-EDB server. Execution oracles can be used for reporting useful information about
Argennon transactions such as accessed AVM heap or code area locations, exact amount of execution cost,
and so on.

@@

\begin{itemize}
    \item Maximum internal execution cost
    \item Maximum external execution cost
    \item A list of heap/code-area locations for reading
    \item A list of heap locations for writing
    \item A list of heap chunks it will deallocate (if any)
    \item A list of methods it will delete (if any)
    \item Number and size of heap chunks it will allocate (if any)
    \item Number and size of method bytecodes it will allocate (if any)
\end{itemize}

@@

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,
    label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST bttp://dapp.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 77

    {
        "name": "Grant",
        "recipient": "0x24.0x8f.0x29.0xa1",
        "amount": 25000,
        "sig"= "2a36Gtrw249wQCD70nWY49d"
    }
caps:
    internal: 2500000 # maximum number of AVM execution clocks
    external: 1000000
    read: [(2654,3),(15642,0),(15642,1),(15642,3)]
    write: [(15642,0),(20154,0),(20154,1)]
\end{lstlisting}

\subsection{Authorization}\label{subsec:txn-auth}

Argennon transactions do not have a sender. The authorization of the requested operation is always done by checking the
digital signatures that are provided as a part of the HTTP request to the \texttt{dispatcher} method.

While every block of the Argennon blockchain stores the commitment of the transaction list, Argennon does not enforce
storage of the transaction history. To be able to detect replay attacks, we require
every signature that a user creates to have a nonce. This nonce consists of the issuance round of the signature
and a sequence number: \texttt{(issuance,\ sequence)}. When a user creates more than one signature in a round, he
must sequence his signatures starting from 0 (i.e.~the sequence number restarts from 0 in every round). We define
a maximum lifetime for signatures, so a signature is invalid if \texttt{currentRound - issuance > maxLifeTime} or
if a signature of the same user with a bigger or equal nonce is already used
(i.e.~is recorded in the blockchain). A nonce is bigger than another nonce if it has an older issuance. If two
nonces have an equal issuance, the nonce with the bigger sequence number will be considered bigger.

To be able to detect invalid signatures, we keep the maximum nonce of used digital signatures per user. This information
is stored in the ARG smart contract and when the difference between \texttt{issuance} component of the nonce and
the current round becomes bigger than the maximum allowed lifetime of a signature, it can be safely
deleted.\footnote{in some conventional
blockchains, the nonce data can never be deleted, even if the account has zero balance and is no longer used.}

\subsection{Transaction Fee}\label{subsec:fee}

Every Argennon transaction is required to pay two types of fees: execution fee, which is paid for executing the
transaction, and storage fee, which is paid for the amount of storage the transaction allocates.

A transaction pays
its fees by providing digital signatures of one or more accounts, authorizing the transfer of the amount of fee in
ARGs from one or more accounts to the fee sink accounts. This fee is transferred by the first
\texttt{i\_invoke\_dispatcher} instruction of the transaction.

\note{An Argennon transaction always pays all of its proposed fee, no matter how much of its predefined resources
were not used during the final emulation. This will incentivize users to report the resource usage of their
transactions more accurately.}

>>>>

An Argennon transaction consist of an HTTP request made by a user to an Argennon application, a resource
declaration object and a list of signed messages. Transactions can only be
issued by users and applications can not create transactions. An Argennon transaction is also called
an \emph{external request}.

@@

@@

\begin{itemize}
    \item Maximum AscEE clocks
    \item The list of applications the request will call
    \item The list of access blocks the request needs
    \item \texttt{maxSize} for chunks it wants to expand
    \item \texttt{minSize} for chunks it wants to shrink
    \item A list of applications it will update (if any)
\end{itemize}

@@

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,
    label={lst:txn-example}]
---
request: |
    PATCH /balances/0x95ab HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 46

    {"to":0xaabc,"amount":1399,"sig":0}

messages:
   - issuer: 0x95ab000000000000
     msg: {"to":0xaabc000000000000,"amount":1399,"forApp":0x100000000000000,"nonce":11}
     sig: LNUC49Lhyz702uszzNcfaU3BhPIbdaSgzqDUKzbJzLPTlFS2J9GzHl-cDKb

caps:
    maxClocks: 150 # maximum number of AVM execution clocks
    apps: [1,124.16]
    read: [(2654,3),(15642,0),(15642,1),(15642,3)]
    write: [(15642,0),(20154,0),(20154,1)]
\end{lstlisting}

### 2022-04-16 tex/sections/incentive.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Remove outdated parts
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

@@

\subsection{Incentives for ZK-EDB Servers}\label{subsec:zk-edb-servers}

The incentive mechanism for ZK-EDB servers should have the following properties:

\begin{itemize}
    \item It incentivizes storing all storage pages and not only those pages that are used more frequently.
    \item It incentivizes ZK-EDB servers to actively provide the required storage pages for validators.
    \item Making more accounts will not provide any advantage for a ZK-EDB server.
\end{itemize}

For our incentive mechanism, we require that every time a validator receives a storage page from a ZK-EDB, after
validating the data, he give a receipt to the ZK-EDB server. In this receipt the validator signs the
following information:

\begin{itemize}
    \item \texttt{ownerAddr}: the account address of the ZK-EDB server.
    \item \texttt{receivedPageID}: the ID of the received page.
    \item \texttt{round}: the current block number.
\end{itemize}

\note{In a round, an honest validator never gives a receipt for an identical page to two different ZK-EDB servers.}

To incentivize ZK-EDB servers, a lottery will be held every round,\footnote{A round is the time interval between
two consecutive blocks.} and a predefined amount of ARGs from
\texttt{dbFeeSink} account will be distributed between winners as a prize. This prize will be divided equally
between all \emph{winning tickets} of the lottery.

\note{One ZK-EDB server could own multiple winning tickets in a round.}

@@

\begin{itemize}
    \item The signer was a member of the validators' committee of the block $r - 1$ and signed the block certificate.
    \item The page in the receipt was needed for validating the \textbf{previous} block.
    \item The receipt round number is $r - 1$.
    \item The signer did not sign a receipt for the same storage page for two different ZK-EDB servers in
    the previous round.
\end{itemize}
For selecting the winning receipts we could use a random generator:
\begin{verbatim}
IF random(seed|validatorPK|receivedPageID) < winProbability THEN
    the receipt issued by validatorPK for receivedPageID is a winner
\end{verbatim}
\begin{itemize}
    \item \texttt{random()} produces uniform random numbers between 0 and 1, using its input argument as a seed.
    \item \texttt{validatorPK} is the public key of the signer of the receipt.
    \item \texttt{receivedPageID} is the ID of the storage page that the receipt was issued for.
    \item \texttt{winProbability} is the probability of winning in every round.
    \item \texttt{seed} is the current block seed.
    \item \texttt{|} is a concatenation operator.
\end{itemize}

Also, based on the current block seed, a random storage page is
selected as the challenge of the round. A ZK-EDB server that owns a winning receipt needs to broadcast a \emph{winning
ticket} to claim his prize. The winning ticket consists of a winning receipt and a \emph{solution} to the round
challenge. Solving a round challenge requires the content of the storage page which was selected as the round
challenge. This will encourage ZK-EDB servers to store all storage pages.

@@

The winning tickets of the lottery of round $r$ need to be included in the block of the round $r$,
otherwise they will be considered expired. Validation and prize distribution for the winning tickets of round
$r$ will be done in the round $r + 1$. This way, \textbf{the content of the challenge page could be
kept secret during the lottery round.} Every winning ticket will get an equal share of the lottery prize.

>>>>

\subsection{Fees}\label{subsec:fees}

The Argennon protocol does not explicitly define any fees for normal transactions. Only for high priority
transactions a fixed fee is determined by the governance system (See Section ...). Because the protection of the
Argennon network against spams and DOS attacks is mostly done by the delegates, they are also responsible for
collecting transaction fees. A good fee collection policy could considerably increase the chance of delegates for
being reelected in the
next round, therefore they are incentivized to use creative and effective methods\footnote{For example, they may
allow a limited number of free transactions per month for every account.}.

By the concept of request attachments, the Argennon protocol provides a method
for trust-less fee payment. A user can simply define the transaction that he wants to pay fees for, as the attachment
of the fee payment transaction. That way the fee payment transaction will be performed only if the attached
transaction is also included in the same block. However, it should be noted that trust-less fee payment is not
enforced by the protocol.

While transaction fee is not enforced by the Argennon protocol another type of fee is mandatory: the
\emph{storage fee}. The Argennon protocol requires that a storage fee is paid for every block of the Argennon
blockchain. This fee must be paid by the delegates, and its amount depends on the storage overhead that the new block
is imposing on the Argennon state. The exact amount of this fee is determined by the ADAGs.

@@

\subsection{Incentives for PV-DB Servers}\label{subsec:PV-DB-servers}

The incentive mechanism for PV-DB servers should have the following properties:

\begin{itemize}
    \item It incentivizes storing all storage pages and not only those pages that are used more frequently.
    \item It incentivizes PV-DB servers to actively provide the required storage pages for validators.
    \item Making more accounts will not provide any advantage for a PV-DB server.
\end{itemize}

For our incentive mechanism, we require that every time a validator receives a storage page from a PV-DB, after
validating the data, he give a receipt to the PV-DB server. In this receipt the validator signs the
following information:

\begin{itemize}
    \item \texttt{ownerAddr}: the account address of the PV-DB server.
    \item \texttt{receivedPageID}: the ID of the received page.
    \item \texttt{round}: the current block number.
\end{itemize}

\note{In a round, an honest validator never gives a receipt for an identical page to two different PV-DB servers.}

To incentivize PV-DB servers, a lottery will be held every round,\footnote{A round is the time interval between
two consecutive blocks.} and a predefined amount of ARGs from
\texttt{dbFeeSink} account will be distributed between winners as a prize. This prize will be divided equally
between all \emph{winning tickets} of the lottery.

\note{One PV-DB server could own multiple winning tickets in a round.}

@@

\begin{itemize}
    \item The signer was a member of the validators' committee of the block $r - 1$ and signed the block certificate.
    \item The page in the receipt was needed for validating the \textbf{previous} block.
    \item The receipt round number is $r - 1$.
    \item The signer did not sign a receipt for the same storage page for two different PV-DB servers in
    the previous round.
\end{itemize}
For selecting the winning receipts we could use a random generator:
\begin{verbatim}
IF random(seed|validatorPK|receivedPageID) < winProbability THEN
    the receipt issued by validatorPK for receivedPageID is a winner
\end{verbatim}
\begin{itemize}
    \item \texttt{random()} produces uniform random numbers between 0 and 1, using its input argument as a seed.
    \item \texttt{validatorPK} is the public key of the signer of the receipt.
    \item \texttt{receivedPageID} is the ID of the storage page that the receipt was issued for.
    \item \texttt{winProbability} is the probability of winning in every round.
    \item \texttt{seed} is the current block seed.
    \item \texttt{|} is the concatenation operator.
\end{itemize}

Also, based on the current block seed, a random storage page is
selected as the challenge of the round. A PV-DB server that owns a winning receipt needs to broadcast a \emph{winning
ticket} to claim his prize. The winning ticket consists of a winning receipt and a \emph{solution} to the round
challenge. Solving a round challenge requires the content of the storage page which was selected as the round
challenge. This will encourage PV-DB servers to store all storage pages.

@@

The winning tickets of the lottery of round $r$ need to be included in the block of the round $r$,
otherwise they will be considered expired. However, finalizing and prize distribution for the winning tickets
should be done in a later round. This way, \textbf{the content of the challenge page could be
kept secret during the lottery round.} Every winning ticket will get an equal share of the lottery prize.
